Adopting agile in the large: motivations, success factors and challenges

### 2014-05-16 journal/article.tex
Editing and summary box: Investing in transformation

\begin{table}[b]
    \begin{tabular}{ l l }
        \toprule
        Types of change resistance           &  References  \\
        \midrule
        General resistance to change         &  P14, P18, P22, P44, P45   \\
        Skepticism towards a new model       &  P5, P8, P9, P18, P36, P46 \\
        Top down mandate creates resistance  &  P2, P12, P37, P49 \\
        Management not willing to change     &  P2, P3, P6, P49 \\
        \bottomrule
    \end{tabular}
    \caption{Types of change resistance reported in studies}
    \label{table:challenges_changeresistance}
\end{table}

@@

It is clear that changing the way of working will create some costs for the
organization. Problems will ensue if there is no intention to allow resources
for the transformation. Examples on this was lack of investment in training, and
keeping people allocated to tasks from the old arrangement. In some cases the
transformation was impeded when work spaces could not be updated.

@@

Lack of activities supporting a transformation was an evident problem. Training
and coaching were often short of resources, but underbudgeting these activities
may seriously hamper the transformation.
Hajjdiab [P20] describes how reluctance of management to invest in training
caused teams to be ill prepared for the agile transformation effort, and
eventually resulted in ending the use of agile methods. As a less dramatic
outcome of shortened training was lower motivation [P45].

Arranging proper coaching was a particular problem in many organizations. It is
critical to coach teams in their real work environment as a mindset change is
difficult to achieve by only attending training sessions. In large organizations
where numerous teams needed to be coached the demand often exceeded the capacity
of available coaches [P1, P6, P23, P49]. Lack of coaching was also attributed as
a reason why the success of pilot teams could not be repeated when agile was
adopted more widely [P9, P45].
Silva and Doss [P47] described that when it was hard to fill the coaching
positions people less seasoned in agile were appointed as coaches, which risked
that agile practices would not be taught correctly.

@@

Even though the organization was in a state of transformation the workload of
teams was not always adjusted to facilitate the process.
Some organizations started their agile journey in a state where people were
overcommitted, but it was later realized that when people are overloaded they
will not be able to changing their behavior and learn new ways of working [P37,
P42]. Cowan [P11] describes how time was allocated for tending to old
commitments. However, even when there was preparation for extra work people with
specific expertise became overloaded. After time it was realized that
overcommitment must be reduced by allowing to shift excess work for later time
[P11]. In another case management forced people to remain committed to firm
deadlines, even midst in the organizational transformation [P21]. The engagement
in old commitments and tasks resulted in ignoring new practices introduced by
agile, and eventually the agile method was breaking down [P21]. Spayd [P49] also
describes how senior management pressed teams to deliver what the customer had
been promised, regardless of what the current velocity of development predicted.
For one part the pressure to deliver interfered with the transformation, but it
was also forcing a change in the old way of working [P49].

>>>>

\begin{table}[b]
    \begin{tabular}{ l l }
        \toprule
        Types of change resistance           &  Described in  \\
        \midrule
        General resistance to change         &  P14, P18, P22, P44, P45   \\
        Skepticism towards a new model       &  P5, P8, P9, P18, P36, P46 \\
        Top down mandate creates resistance  &  P2, P12, P37, P49 \\
        Management not willing to change     &  P2, P3, P6, P49 \\
        \bottomrule
    \end{tabular}
    \caption{Types of change resistance reported in studies}
    \label{table:challenges_changeresistance}
\end{table}

@@

It is clear that changing the way of working will create some costs for the
organization. Problems will ensue if there is no intention to allow resources
for the transformation. Table \ref{table:challenges_lackofinvestment} presents
investments and resourcing arrangements that were witheld, and which caused
problems in transformation.

\begin{table}[b]
    \begin{tabular}{ l l }
        \toprule
        Factors of investment and resourcing  &  Described in \\
        \midrule
        Lack of coaching                      &  P1, P6, P23, P45, P47, P49  \\
        Lack of training                      &  P11, P20, P45  \\
        Excessive commitment of people        &  P37, P42, P49  \\
        Old commitments are kept              &  P11, P21  \\
        Physical spaces can not be rearranged  &  P6, P29, P36, P49  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investment and resourcing factors that affect
             transformation negatively}
    \label{table:challenges_lackofinvestment}
\end{table}

@@

Training and coaching are direct investments in transformation and their lack is
an evident problem. These activities were still underbudgeted, which
created difficulties in the transformation [P11].
Hajjdiab [P20] describes how reluctance of management to invest in training
caused teams to be ill prepared for the agile transformation effort, which
eventually resulted in ending the use of agile methods. As a less dramatic
outcome of too little training was lower motivation [P45].

Arranging proper coaching was a particular problem in many organizations. It is
critical to coach teams in their real work environment as a proper change in
mindset is difficult to achieve by only attending training sessions. [P9, P23]
In large
organizations where numerous teams needed to be coached the demand often
exceeded the capacity of available coaches [P1, P6, P23, P49]. Lack of coaching
was also attributed as a reason why the success of pilot teams could not be
repeated when agile was adopted more widely [P9, P45].
Silva and Doss [P47] described that when it was hard to fill the coaching
positions people less seasoned in agile were appointed as coaches, which risked
that agile practices would not be taught correctly.

@@

Even though the organization was in a state of transformation the workload of
teams was not always adjusted to facilitate the process.
Some organizations started their agile journey in a state where people were
overcommitted. It was later realized that when people are overloaded they will
not be able to changing their behavior and learn new ways of working [P37, P42].
Spayd [P49] also describes how senior management pressed teams to deliver what
the customer had been promised, regardless of what the current velocity of
development predicted. For one part the pressure to deliver interfered with the
transformation, but it was also forcing a change in the old way of working
[P49].

In one case management forced people to remain committed to firm deadlines, even
midst in the organizational transformation [P21]. The engagement in old
commitments and tasks resulted in ignoring new practices introduced by agile,
and eventually the agile method was breaking down [P21].
Cowan [P11] describes how time was allocated for tending to old commitments.
However, even when there was preparation for extra work people with specific
expertise became overloaded. After time it was realized that overcommitment must
be reduced by allowing to shift excess work for later time [P11].
